\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Understanding Driver Behavior: Studies on NYC Taxi Data}

### 2015-05-11 Report/article_2.tex
straggling citation
final

\noindent Using all data on NYC taxi trips and fares from 2010 and 2013 we perform a series of studies to understand motivating factors behind driver behavior as well as outcomes from those incentives. In order to analyze this large dataset ($\approx$14GB), we employ a number of big data processing technologies that work on the Hadoop framework: Hive, Spark, and MapReduce programs.  We present our findings, issues encountered, and experimental setup. Of these findings, the most notable include: there are outlier drivers who are on average more productive per day, the sensitivity of fares to environment variables are seemingly invariant, the distribution of actual to predicted fares implies a number of overcharges that should be investigated, drivers can expect better tips from passenger drop-off to certain areas, and previous tips affect driver behavior for the next trip.

@@

\noindent which is distributed $F(k, N_{2010} + N_{2013}-2k)$. \cite{CHOW}

>>>>

\noindent Using all data on NYC taxi trips and fares from 2010 and 2013 we perform a series of studies to understand motivating factors behind driver behavior as well as outcomes from those incentives. In order to analyze this large dataset ($\approx$14GB), we employ a number of big data processing technologies that work on the Hadoop framework: Spark and MapReduce programs.  We present our findings, issues encountered, and experimental setup. Of these findings, the most notable include: there are outlier drivers who are on average more productive per day, the sensitivity of fares to environment variables are seemingly invariant, the distribution of actual to predicted fares implies a number of overcharges that should be investigated, drivers can expect better tips from passenger drop-off to certain areas, and previous tips affect driver behavior for the next trip.

@@

\noindent which is distributed $F(k, N_{2010} + N_{2013}-2k)$.
